Manuscript

### 2015-03-16 inst/simulation/manuscript.Rmd
...

meanPopulationSizes  <- getMeanPopulationSizes(cutoffPopulationSizes(populationSizes, cutoff, models=modelNames[1]))
logPopulationSizes <- getLogPopulationSizes(cutoffPopulationSizes(populationSizes, cutoff, models=modelNames[1]))
logMeanPopulationSizes  <- getMeanPopulationSizes(logPopulationSizes)

meanPopulationSizes2000  <- getMeanPopulationSizes(cutoffPopulationSizes(populationSizes2000, 10*cutoff, models=modelNames[1]))
logPopulationSizes2000 <- getLogPopulationSizes(cutoffPopulationSizes(populationSizes2000, 10*cutoff, models=modelNames[1]))
logMeanPopulationSizes2000  <- getMeanPopulationSizes(logPopulationSizes2000)

meanPopulationSizes10Days  <- getMeanPopulationSizes(cutoffPopulationSizes(populationSizes10Days, cutoff, models=modelNames[1]))
logPopulationSizes10Days <- getLogPopulationSizes(cutoffPopulationSizes(populationSizes10Days, cutoff, models=modelNames[1]))
logMeanPopulationSizes10Days  <- getMeanPopulationSizes(logPopulationSizes10Days)
```

@@

table1 <- getPopulationSizesTable(populationSizes, meanPopulationSizes, overEstimate=cutoff, models=modelNames[1])
logTable1 <- getPopulationSizesTable(logPopulationSizes, logMeanPopulationSizes, overEstimate=log10(cutoff+1), models=modelNames[1])
logTable1$Failed <- table1$Failed

table2 <- getPopulationSizesTable(populationSizes2000, meanPopulationSizes2000, overEstimate=10*cutoff, models=modelNames[1])
logTable2 <- getPopulationSizesTable(logPopulationSizes2000, logMeanPopulationSizes2000, overEstimate=log10(10*cutoff+1), models=modelNames[1])
logTable2$Failed <- table2$Failed

table3 <- getPopulationSizesTable(populationSizes10Days, meanPopulationSizes10Days, overEstimate=cutoff, models=modelNames[1])
logTable3 <- getPopulationSizesTable(logPopulationSizes10Days, logMeanPopulationSizes10Days, overEstimate=log10(cutoff+1), models=modelNames[1])
logTable3$Failed <- table3$Failed

@@

plotPopulationSizesTable <- function(logTable) {
  library(reshape2)
  facet_labeller <- function(variable, value) {
    measured <- list(Slope=expression(beta), R2=expression(R^2), EstTrue=expression(alpha), Failed="Failed (%)")
    print(paste0(variable,"=",value))
    if (variable=="variable") return(measured[value])
    if (variable=="Case") return(paste("Case", value))
  }
  x <- melt(logTable, id.vars=c("Scenario", "Model", "Case"), measure.vars=c("Slope", "R2", "EstTrue", "Failed"))
  bestFit <- data.frame(variable=unique(x$variable), y=c(1, 1, 0, 0))
  errorBars <- x
  errorBars$value <- NA
  errorBars$value[errorBars$variable=="Slope"] <- logTable$Slope
  errorBars$qmin[errorBars$variable=="Slope"] <- logTable$Slope-logTable$SlopeSD
  errorBars$qmax[errorBars$variable=="Slope"] <- logTable$Slope+logTable$SlopeSD
  errorBars$value[errorBars$variable=="EstTrue"] <- logTable$EstTrue
  errorBars$qmin[errorBars$variable=="EstTrue"] <- logTable$EstTrueMin
  errorBars$qmax[errorBars$variable=="EstTrue"] <- logTable$EstTrueMax

@@

```{r figure-3sample}
xlim <- log10(c(10,800)); ylim <- xlim
logPopulationSizesSample <- subset(logPopulationSizes, scenario == "A")
logPopulationSizesSample$modelName <- prettyModelName(logPopulationSizesSample$modelName)
logPopulationSizesSample <- rbind(
  subset(logPopulationSizesSample, modelName=="ST"),
  subset(logPopulationSizesSample, modelName=="T1"),
  subset(logPopulationSizesSample, modelName=="T2"),
  subset(logPopulationSizesSample, modelName=="FMP"))

@@

pc1 <- getPopulationCorrelations(scenarios=scenarios, modelNames=modelNames[1], cutoff=cutoff)
pc2a <- getPopulationCorrelations(scenarios="Acombined", modelNames=modelNames[1], cutoff=cutoff)
pc2b <- getPopulationCorrelations(scenarios="Bcombined", modelNames=modelNames[1], cutoff=cutoff)
pc2c <- getPopulationCorrelations(scenarios="Ccombined", modelNames=modelNames[1], cutoff=cutoff)
pc2d <- getPopulationCorrelations(scenarios="Dcombined", modelNames=modelNames[1], cutoff=cutoff)
pc2e <- getPopulationCorrelations(scenarios="Ecombined", modelNames=modelNames[1], cutoff=cutoff)
pc2f <- getPopulationCorrelations(scenarios="Fcombined", modelNames=modelNames[1], cutoff=cutoff)
pc2 <- rbind(pc2a,pc2b,pc2c,pc2d,pc2e,pc2f)
pc3 <- getPopulationCorrelations(scenarios=paste0(scenarios, "10days"), modelNames=modelNames[1], cutoff=cutoff)

>>>>

meanPopulationSizes  <- getMeanPopulationSizes(cutoffPopulationSizes(populationSizes, cutoff, models=modelNames[c(1,3,5)]))
logPopulationSizes <- getLogPopulationSizes(cutoffPopulationSizes(populationSizes, cutoff, models=modelNames[c(1,3,5)]))
logMeanPopulationSizes  <- getMeanPopulationSizes(logPopulationSizes)

meanPopulationSizes2000  <- getMeanPopulationSizes(cutoffPopulationSizes(populationSizes2000, 10*cutoff, models=modelNames[c(1,3,5)]))
logPopulationSizes2000 <- getLogPopulationSizes(cutoffPopulationSizes(populationSizes2000, 10*cutoff, models=modelNames[c(1,3,5)]))
logMeanPopulationSizes2000  <- getMeanPopulationSizes(logPopulationSizes2000)

meanPopulationSizes10Days  <- getMeanPopulationSizes(cutoffPopulationSizes(populationSizes10Days, cutoff, models=modelNames[c(1,3,5)]))
logPopulationSizes10Days <- getLogPopulationSizes(cutoffPopulationSizes(populationSizes10Days, cutoff, models=modelNames[c(1,3,5)]))
logMeanPopulationSizes10Days  <- getMeanPopulationSizes(logPopulationSizes10Days)
```

@@

#x <- subset(populationSizes, modelName=="SmoothModelMean-nbinomial-ar1-priors1" & Scenario=="C")
#y <- lm(Estimated~Observed, x)

table1 <- getPopulationSizesTable(populationSizes, meanPopulationSizes, overEstimate=cutoff, models=modelNames[c(1,3,5)])
logTable1 <- getPopulationSizesTable(logPopulationSizes, logMeanPopulationSizes, overEstimate=log10(cutoff+1), models=modelNames[1])
logTable1$Failed <- table1$Failed

table2 <- getPopulationSizesTable(populationSizes2000, meanPopulationSizes2000, overEstimate=10*cutoff, models=modelNames[c(1,3,5)])
logTable2 <- getPopulationSizesTable(logPopulationSizes2000, logMeanPopulationSizes2000, overEstimate=log10(10*cutoff+1), models=modelNames[1])
logTable2$Failed <- table2$Failed

table3 <- getPopulationSizesTable(populationSizes10Days, meanPopulationSizes10Days, overEstimate=cutoff, models=modelNames[c(1,3,5)])
logTable3 <- getPopulationSizesTable(logPopulationSizes10Days, logMeanPopulationSizes10Days, overEstimate=log10(cutoff+1), models=modelNames[1])
logTable3$Failed <- table3$Failed

@@

plotPopulationSizesTable <- function(logTable) {
  library(reshape2)
  facet_labeller <- function(variable, value) {
    measured <- list(Slope=expression(beta), R2=expression(R^2), EstTrue=expression(alpha), Failed="Failed (%)")
    print(paste0(variable,"=",value))
    if (variable=="variable") return(measured[value])
    if (variable=="Case") return(paste("Case", value))
  }
  x <- melt(logTable, id.vars=c("Scenario", "Model", "Case"), measure.vars=c("Slope", "R2", "EstTrue", "Failed"))
  bestFit <- data.frame(variable=unique(x$variable), y=c(1, 1, 0, 0))
  errorBars <- x
  errorBars$value <- NA
  #errorBars$value[errorBars$variable=="Slope"] <- logTable$Slope
  #errorBars$qmin[errorBars$variable=="Slope"] <- logTable$Slope-logTable$SlopeSD
  #errorBars$qmax[errorBars$variable=="Slope"] <- logTable$Slope+logTable$SlopeSD
  errorBars$value[errorBars$variable=="EstTrue"] <- logTable$EstTrue
  errorBars$qmin[errorBars$variable=="EstTrue"] <- logTable$EstTrueMin
  errorBars$qmax[errorBars$variable=="EstTrue"] <- logTable$EstTrueMax

@@

```{r figure-3sample}
xlim <- log10(c(30,800)); ylim <- xlim
logPopulationSizesSample <- subset(logPopulationSizes, scenario == "A")
logPopulationSizesSample$modelName <- prettyModelName(logPopulationSizesSample$modelName)
logPopulationSizesSample <- rbind(
  subset(logPopulationSizesSample, modelName=="ST"),
  subset(logPopulationSizesSample, modelName=="T1"),
  subset(logPopulationSizesSample, modelName=="T2"),
  subset(logPopulationSizesSample, modelName=="FMP"))

@@

pc1a <- getPopulationCorrelations(scenarios="A", modelNames=modelNames[1], cutoff=cutoff)
pc1b <- getPopulationCorrelations(scenarios="B", modelNames=modelNames[1], cutoff=cutoff)
pc1c <- getPopulationCorrelations(scenarios="C", modelNames=modelNames[1], cutoff=cutoff)
pc1d <- getPopulationCorrelations(scenarios="D", modelNames=modelNames[1], cutoff=cutoff)
pc1e <- getPopulationCorrelations(scenarios="E", modelNames=modelNames[1], cutoff=cutoff)
pc1f <- getPopulationCorrelations(scenarios="F", modelNames=modelNames[1], cutoff=cutoff)
pc1 <- rbind(pc1a,pc1b,pc1c,pc1d,pc1e,pc1f)
pc2a <- getPopulationCorrelations(scenarios="Acombined", modelNames=modelNames[1], cutoff=10*cutoff)
pc2b <- getPopulationCorrelations(scenarios="Bcombined", modelNames=modelNames[1], cutoff=10*cutoff)
pc2c <- getPopulationCorrelations(scenarios="Ccombined", modelNames=modelNames[1], cutoff=10*cutoff)
pc2d <- getPopulationCorrelations(scenarios="Dcombined", modelNames=modelNames[1], cutoff=10*cutoff)
pc2e <- getPopulationCorrelations(scenarios="Ecombined", modelNames=modelNames[1], cutoff=10*cutoff)
pc2f <- getPopulationCorrelations(scenarios="Fcombined", modelNames=modelNames[1], cutoff=10*cutoff)
pc2 <- rbind(pc2a,pc2b,pc2c,pc2d,pc2e,pc2f)
pc3 <- getPopulationCorrelations(scenarios=paste0(scenarios, "10days"), modelNames=modelNames[1], cutoff=cutoff)
